Are iPhone users more secure when using mobile enterprise systems?

### 2021-04-25 outputs/paper/paper.Rmd
update

```{r page1, echo=FALSE, fig.cap="Screen capture of the first part of the Survey.", out.width = '70%', fig.align="center"} 
library(here)
knitr::include_graphics(here::here("outputs/image/questionnaire1.png"))
```

## Appendix B 
The first 20 rows of raw data which will be used in regression is shown in the Table below. (Table \@ref(tab:rowdata))
#plot row data set in table
```{r rowdata, echo=FALSE}
  head(clean_data,20)%>%
  kableExtra::kbl(caption = "First 100 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()
```
\newpage

>>>>

```{r page1, echo=FALSE, fig.cap="Screen capture of the first part of the Survey.", out.width = '70%', fig.align="center"} 
knitr::include_graphics(here::here("outputs/paper/image/image1.png"))
```

## Appendix B 
The first 100 rows of raw data which will be used in regression is shown in the Table below. (Table \@ref(tab:rowdata))
```{r rowdata, echo=FALSE}
  head(clean_data,100)%>%
  kableExtra::kbl(caption = "First 100 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()
```
\newpage
